```{r setup-victors, eval=TRUE, include=FALSE, echo=FALSE}
# Function to get Attribute Fields
getAttributeField <- function (x, field, attrsep = ";") { 
  s = strsplit(x, split = attrsep, fixed = TRUE) 
  sapply(s, function(atts) { 
    a = strsplit(atts, split = "=", fixed = TRUE) 
    m = match(field, sapply(a, "[", 1)) 
    if (!is.na(m)) { rv = a[[m]][2] 
    } 
    else { 
      rv = as.character(NA) 
    } 
    return(rv) 
  }) 
}

# Function do get URLs for DATATABLE
vf_id_url_DT <- function (x) {
  
  id <-  x[5]
  url <- paste0("http://www.phidias.us/victors/gene_detail.php?c_mc_victor_id=", id)
  url <- paste0("<a  target=_blank href=", url, ">", id,"</a>" )
  
  return(url)
}

# Get Victors Metadata
victors_meta <- read.delim("/work/victors/victors_metadata.tsv")
#victors_meta <- read.delim("/Users/falmeida/Downloads/victors_metadata.tsv")
```

```{r parsing-db-victors, eval=TRUE, include=FALSE, echo=FALSE}
# Parse BLAST
blast <- victors_blast %>% select(qseqid, stitle)
blast <- separate(blast, stitle, c("vf_header", "Description"), sep = " ", extra = "merge")
blast <- separate(blast, vf_header, c("db", "Gene Name", "ref", "VF ID"), sep = "~~~", extra = "merge")
blast <- separate(blast, `VF ID`, c("db", "VF ID"), sep = "_", extra = "merge")
blast$`Gene Name` <- gsub(blast$`Gene Name`, pattern = "_", replacement = " ")

# Merge annotation with metadata
victors_full <- merge.data.frame(blast, victors_meta, by.x = "VF ID", by.y = "NCBI.Protein.GI")
victors_full <- victors_full[ !duplicated(victors_full$qseqid), ]

# Create ID Column
gff$ID <- getAttributeField(as.character(gff$V9), "ID", ";")

# To upper
gff$ID <- toupper(gff$ID)

# Merge with GFF
victors_full <- merge.data.frame(victors_full, gff, by.x = "qseqid", by.y = "ID")

# Create Position Column
victors_full$position <- paste(victors_full$V1, ":", victors_full$V4, "-", victors_full$V5, sep = "")

# Create DF for kable
blast <- victors_full %>% select(qseqid, Gene.Name, Protein.Name, Description, Protegen.ID, position)

# Get urls
ids <- blast$Protegen.ID
urls <- lapply(ids, function(x){paste0("http://www.phidias.us/victors/gene_detail.php?c_mc_victor_id=", x)})
```

All query genes predicted by Prokka that have a match in Victors database are described in Table \@ref(tab:write-table-victors). In order to make further investigations easier, all genes are linked to its matches in Victors database.

> Victors database is protein-only thus genes are scanned via blastp. Victors is a new database and focused in proteins that are important in the interaction pathogen-host, thus it may contain proteins that you have never heard about.

<caption>(#tab:write-table-victors) Virulence factors annotated using the Victors database via BLASTp</caption>
```{r}
# Produce Table
colnames(blast) <- c("Query Protein ID", "Gene Name", "Product", "Description", "Database ID", "Query Protein Coordinates")
blast$`Database ID` <- apply(blast, 1, vf_id_url_DT)
## The conversion
blast[sapply(blast, is.character)] <- lapply(blast[sapply(blast, is.character)], as.factor)
datatable(blast,
          escape = FALSE,
          filter = 'top',
          options = dt_opt_lst,
          extensions = 'Buttons',
          rownames = T)
```