```{r setup-phast, eval=TRUE, include=FALSE, echo=FALSE}
# Fucntions

## Function to get Attribute Fields
getAttributeField <- function (x, field, attrsep = ";") { 
  s = strsplit(x, split = attrsep, fixed = TRUE) 
  sapply(s, function(atts) { 
    a = strsplit(atts, split = "=", fixed = TRUE) 
    m = match(field, sapply(a, "[", 1)) 
    if (!is.na(m)) { rv = a[[m]][2] 
    } 
    else { 
      rv = as.character(NA) 
    } 
    return(rv) 
  }) 
}
```

All prophage genes from PHAST database that had good alignments to the genes of the query genome are summarized in Table \@ref(tab:phast-table). The protein sequences of these genes were aligned against the gene sequences predicted by Prokka via BLASTp. They are all available in the genome browser provided. A good way to interrogate this annotation is to visualize the putative prophage regions predicted by phigaro and phispy interpolating it with the prophage gene annotation provided with phast database.

> Unfortunately, PHASTER database have no searchable interface to visualize its prophages. Therefore, this table has no links to external sources.

<caption>(#tab:phast-table) Prophage genes annotated using PHAST database via BLASTp</caption>
```{r phast-table}
# Create ID Column
gff$ID <- getAttributeField(as.character(gff$V9), "ID", ";")

# To upper
gff$ID <- toupper(gff$ID)

# Parse BLAST
blast <- phast_prot_blast %>% select(-sseqid)
blast <- separate(blast, stitle, c("header", "Description"), sep = " ", extra = "merge")
blast <- separate(blast, header, c("db", "product", "ref", "phast_id"), sep = "~~~", extra = "merge")
blast$prophage <- sapply(str_split(blast$Description, "\\|"), head, 1)
blast$prophage <- gsub(blast$prophage, pattern = "-..$", replacement = "")
blast$product <- gsub(blast$product, pattern = "_", replacement = " ")

# Data Complete
full_info <- merge.data.frame(blast, gff, by.x = "qseqid", by.y = "ID", all = TRUE)

# Create Position Column
full_info$position <- paste(full_info$V1, ":", full_info$V4, "-", full_info$V5, sep = "")
full_info <- full_info %>% select(prophage, Description, qseqid, product, position) %>%
  arrange(prophage) %>% filter(prophage != "" & Description != "")
colnames(full_info) <- c("Prophage of origin", "Description", "Query protein", "Product", "Genomic Position")

datatable(full_info,
          escape = FALSE,
          filter = 'top',
          options = dt_opt_lst,
          extensions = 'Buttons',
          rownames = F)
```
