The results obtained with RGI tool are summarized in the heatmap produced by the tool itself (Figure \@ref(fig:rgi-summary)). Additionally, the annotation results are also shown in interactive table showing the complete annotation information (Table \@ref(tab:rgi-annotation-table)). They can be roughly divided into two main categories:

1. Perfect hits
    + detects perfect matches to the curated reference sequences and mutations in the CARD
2. Strict hits
    + detects previously unknown variants of known AMR genes, including secondary screen for key mutations, using detection models with CARD's curated similarity cut-offs to ensure the detected variant is likely a functional AMR gene

> **Obs:** CARD RGI tool always tries to annotate functional AMR genes, however, depending on the assembly, a not functional gene may yet be annotated. There for, users are advised to double check genes annotated under **Strict** category.

<br>

<caption>(#tab:rgi-annotation-table) RGI annotation results. The perfect hits are highlighted in yellow while the strict hits in light blue.</caption>
```{r rgi-annotation-table}
# Merge data.frame with GFF
rgi_tsv <- rbind(rgi_perfect, rgi_strict)
colnames(rgi_tsv) <- c("Protein ID", "Cut_Off", "Product", "ARO", "Drug Class", "Resistance Mechanism", "AMR Gene Family")
rgi_tsv <- merge.data.frame(gff, rgi_tsv, by.x = "Prokka_ID", by.y = "Protein ID", all.y = TRUE, all.x = FALSE)

# Get CARD metadata
aro_index <- read.csv("aro_index.tsv", sep = "\t")
aro_index$ARO.Accession <- str_remove(aro_index$ARO.Accession, "ARO:")

# Change Col name
names(aro_index)[names(aro_index) == "ARO.Accession"] <- 'ARO'
aro_index$ARO <- as.integer(aro_index$ARO)
rgi_tsv$ARO <- as.integer(rgi_tsv$ARO)

# Join
rgi_tsv <- merge.data.frame(rgi_tsv, aro_index, by = "ARO", all.x = TRUE)

# Create urls
rgi_tsv$CVTERM.ID <- card_url(rgi_tsv$CVTERM.ID)

# Produce Table
rgi_tsv %>%
  select(Prokka_ID, Product, `AMR Gene Family`, `Drug Class`, `Resistance Mechanism`, CVTERM.ID, `Query Protein Coordinates`, `Cut_Off`) %>%
  arrange(8,1) %>%
  datatable(escape = FALSE,
          filter = 'top',
          options = list(pageLength = 5,
                         lengthMenu = c(5, 10, 15, 20, 50),
                         dom='flrtBip',
                         buttons = c('copy', 'csv', 'excel', 'colvis'),
                         scrollX = TRUE,
                         fixedColumns = FALSE,
                         autoWidth = TRUE,
                         columnDefs = list(list(visible=FALSE, targets=c(7)))),
          extensions = 'Buttons',
          rownames = F) %>%
  formatStyle("Cut_Off", target = 'row', backgroundColor = styleEqual("Perfect", "lightyellow")) %>%
  formatStyle("Cut_Off", target = 'row', backgroundColor = styleEqual("Strict", "lightblue"))
```
<br>

```{r rgi-summary, out.width='60%', fig.align='center', fig.show='hold', fig.cap="RGI's phenotype prediction. AMR genes are listed in alphabetical order and unique resistome profiles are displayed with their frequency. Yellow represents a perfect hit, Blue-green represents a strict hit."}
knitr::include_graphics(params$rgi_heatmap)
```