Below it is summarized the results obtained with RGI. Roughly, it can be divided into two main categories: 

1. Perfect hits
    + detects perfect matches to the curated reference sequences and mutations in the CARD
2. Strict hits
    + detects previously unknown variants of known AMR genes, including secondary screen for key mutations, using detection models with CARD's curated similarity cut-offs to ensure the detected variant is likely a functional AMR gene

**Obs:** CARD RGI tool always tries to annotate functional AMR genes, however, depending on the assembly, a not functional gene may yet be annotated. There for, users are advised to double check genes annotated under **Strict** category.

## Perfect hits

```{r, Perfect_RGI_block, echo=FALSE, results='asis', eval=rgi_perfect_not_null, child='yes_RGI_Perfect.Rmd'}
```

```{r, Perfect_RGI_block2, echo=FALSE, results='asis', eval=rgi_perfect_null, child='no_RGI_Perfect.Rmd'}
```

## Strict hits

```{r, Strict_RGI_block, echo=FALSE, results='asis', eval=rgi_strict_not_null, child='yes_RGI_Strict.Rmd'}
```

```{r, Perfect_RGI_block2, echo=FALSE, results='asis', eval=rgi_strict_null, child='no_RGI_Strict.Rmd'}
```